Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
Added comment

\section{Formalization}
\samuel{Explain concepts on example}
\sergey{subgroup notation, rework the solution definition}
\subsection{Groups, Type-consistency and Constraints}
In this work we focus on spreadsheet data, which is physically one big table, but conceptually often consists of multiple tables, see Figure~\ref{fig:main_example} for an example.
Formally, a table is an $n \times m$ matrix, each table entry is called  a \textit{cell}.

>>>>

\section{Formalization}
\samuel{Explain concepts on example}
\sergey{subgroup notation, rework the solution definition}
\subsection{Groups, Type-consistency and Constraints}
\samuel{Instantiated table... references}
In this work we focus on spreadsheet data, which is physically one big table, but conceptually often consists of multiple tables, see Figure~\ref{fig:main_example} for an example.
Formally, a table is an $n \times m$ matrix, each table entry is called  a \textit{cell}.
